---
title: "Lecture 1 - Intro to Quarto"
author: "Cameron Nemeth"
format:
  html:
    code-fold: true              # code hidden by default, with a toggle button
    code-summary: "Show code"    # customize the button label
editor: visual
warning: false
knitr:
  opts_chunk:
    fig.path: "Week_06/Output/" ## added the ../ because your qmd folder is in your scripts folder so we need to go up one directory and then into your output folder
---

### My document

```{r}
# Load libraries
library(palmerpenguins)
library(tidyverse)
library(kableExtra)


Penguins <- penguins
```

The dataset has `r nrow(Penguins)` rows and `r ncol(Penguins)` columns. The number of distinct species is `r n_distinct(Penguins$species)` that come from `r n_distinct(Penguins$island)` different islands. The mean body mass is `r round(mean(Penguins$body_mass_g, na.rm = TRUE), 2)` g, with a minimum body size of `r round(max(Penguins$body_mass_g, na.rm = TRUE), 2)` g. 

```{r}
#| fig-width: 6
#| fig-height: 4
#| fig-align: "center"
#| label: Penguins
#| fig-cap: "This is my figure"
Plot <- ggplot(Penguins,
                aes(body_mass_g, bill_length_mm)) +
        geom_point() +
        theme_bw()
Plot
```
```{r}
penguins |>
  group_by(species) |>
  summarise(billmean = mean(bill_length_mm, na.rm = TRUE)) |>
  kbl()  |> # make it a kable table
  kable_classic() |> # add a theme
  row_spec(2, bold = TRUE, color = "white", background = "red") |> # highlight row 2
  kable_styling(full_width = FALSE) # don't make it so wide
```

```{r}
#| label: fig-penguin-bill #label things starting with "fig-" and "tbl-" if you are going to call back to them with markdown text to auto-number(see below)
#| fig-cap: "Bill length vs. bill depth for three penguin species."
#| echo: false

ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
  geom_point() +
  scale_color_viridis_d()
```
As shown in @fig-penguin-bill, bill dimensions differ clearly by species.



